Higher-Order unification for free!

### 2024-04-12 paper/main.tex
small change
commented some text

Our encoding provides a third option that addresses all the considerations
mentioned earlier. It capitalizes on the benefit of not requiring the recoding
of the unification algorithm of the object language. Instead, it employs the
unification capabilities of the meta language, facilitated by the various links
we establish to manage ``problematic'' subterms. Moreover, our encoding takes
advantage of indexing algorithms for static clause filtering. It's noteworthy
that we only replace the minimum necessary information with variables,
specifically targeting \maybeeta and \notllambda subterms.

@@

---

Benefits: less work, reuse efficient ho unif (3x faster), indexing,

Future: tabling and static analysis (reuse for ML again).

Very little is Coq specific. Applies to all OL that are not a subsystem of 
HOL, or for ML that are used for meta programming.

>>>>

Our encoding provides a third option that addresses all the considerations
mentioned earlier. It capitalizes on the benefit of not requiring the recoding
of the unification algorithm of the object language. Instead, it employs the
unification capabilities of the meta language, facilitated by the various links
we establish to manage ``problematic'' subterms. Moreover, our encoding takes
advantage of indexing algorithms and mode analysis for static clause filtering. It's noteworthy
that we only replace the minimum necessary information with variables,
specifically targeting \maybeeta and \notllambda subterms.

@@

% ---

% Benefits: less work, reuse efficient ho unif (3x faster), indexing,

% Future: tabling and static analysis (reuse for ML again).

% Very little is Coq specific. Applies to all OL that are not a subsystem of 
% HOL, or for ML that are used for meta programming.
